---
title: "PL Estimation Techniques"
author: "Derek Weix"
date: last-modified
date-format: long
number-sections: true

mainfont: Palatino
sansfont: Palatino

toc: TRUE
toc-location: left

format: 
  html:
    number-sections: false
  
bibliography: "spm.bib"

knitr:
  opts_chunk: 
    warning: false
    message: false

editor: source
---

## Introduction

This document is for use in exploring coding options for PL estimation in the hope of developing a MSPM technique that can use a PLR test to its full potential. Initially we install the required packages.

```{r}
library("tidyverse")
library("mvtnorm")
library("glmnet")
set.seed(123)
```

## @zou_multivariate_2009

They're interested in the problem $H_0: {\boldsymbol \mu} = \mathbf{0}$ versus $H_1: \boldsymbol{\mu} \neq \mathbf{0}$. They consider the following penalized likelihood function
$$
PL(\boldsymbol{\mu}) = n(\bar{\bf{X}}-\boldsymbol{\mu})'\boldsymbol{\Sigma}^{-1}(\bar{\bf{X}}-\boldsymbol{\mu}) + n\gamma\sum_{j=1}^p \frac{1}{|\bar{\bf{X}}^{(j)}|^a}|\boldsymbol{\mu}^{(j)}|
$$
The ALASSO estimator of $\boldsymbol{\mu}$ is
$$
\hat{\boldsymbol{\mu}}_\gamma = \text{arg min} PL(\boldsymbol{\mu}).
$$
This process is demonstrated below for $\boldsymbol \mu = (0.4, 0.05, 0.3)'$, $\boldsymbol{\Sigma} = I_3$, and $\gamma = 0.05$.

```{r}
# MSPM using LASSO (Zou and Qiu, 2009) ------------------------------------
# Parameters
p           <- 3
n_ic        <- 1000
mu_0        <- rep(0, p)
mu_1        <- c(.4, .05, .3)
sigma_0     <- diag(p)
sigma_0_inv <- solve(sigma_0)
gamma       <- .05

# Data generation
X <- rmvnorm(n_ic, mu_1, sigma_0)

# Basic Penalized Likelihood approach
pl <- function(mu_0, X, sigma_0_inv, gamma) {
  n <- nrow(X)
  
  (n*t(colMeans(X)-mu_0) %*% sigma_0_inv %*% (colMeans(X)-mu_0) +
      n*gamma*sum(abs(mu_0/colMeans(X))))
}

mu_hat <- 
  optim(mu_0, pl, X = X, sigma_0_inv = sigma_0_inv, gamma = gamma,
        lower = 0, upper = 1,
        method = "L-BFGS-B")$par

mu_1
mu_hat
```

Then the authors define their LASSO based test statistic as 
$$
\tilde{T}_\gamma = \frac{n(\hat{\boldsymbol{\mu}}_\gamma'\boldsymbol{\Sigma}^{-1}\bar{\bf{X}})^2}{\hat{\boldsymbol{\mu}}_\gamma'\boldsymbol{\Sigma}^{-1}\hat{\boldsymbol{\mu}}_\gamma},
$$
in the case where $\hat{\boldsymbol{\mu}}_\gamma \neq \bf{0}$ and $\tilde{T}_\gamma$ is a negative number otherwise.

```{r}
# LASSO Approach
#glmnet(X)
```
